shrimp_goby_boatnoise

### 2024-11-15 ms_boatnoise_shrimp_goby.Rmd
added table outputs for ms

loc_normal <- 0
scale_normal <- 5

@@

# Plot the PDFs
df <- data.frame(x = x, Logistic = pdf_logistic, Student_t = pdf_student_t, Normal = pdf_normal)
ggplot(df, aes(x)) +
  geom_line(aes(y = Logistic, color = "Logistic(0, 3)")) + # Default priors of Logistic(0,1) have been broadened as these priors seemed too restrictive
  geom_line(aes(y = Student_t, color = "Student_t(3, 0, 2.5)")) +
  geom_line(aes(y = Normal, color = "Normal(0, 5)")) + #For the beta coefficient prior, we will set it to be normally distributed around 0 with an sd of 5, here is the plotted prior distribution 
  labs(title = "Probability Density Functions",
       x = "x",
       y = "Probability Density") +
  scale_color_manual(name = "Distribution", values = c("Logistic(0, 3)" = "blue", "Student_t(3, 0, 2.5)" = "green", "Normal(0, 5)" = "red")) +
  theme_minimal()
```

###2.2.4 Setting priors 
```{r}
#the priors for the intercept have been left as the default and the coefficient priors defined above
priors <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "coi", lb = 0),
            set_prior("normal(0, 5)", class = "b"),
            set_prior("normal(0, 5)", class = "b", dpar = "phi"),
            set_prior("normal(0, 5)", class = "b", dpar = "zoi"),
            set_prior("normal(0, 5)", class = "b", dpar = "coi"))
```

@@

prior_model <- brm(
  prior_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 1000, warmup = 100,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 12345,
  sample_prior = "only",
  file = "prior_check"
)

@@

goby_out_model <- brm(
  goby_out_formula_1,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 12345,
  file = "goby_out_model",

)

@@

goby_out_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  labs(x="Period relative to treatment",
       y="Proportion of time out of burrow") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_text(size = 13),
        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))

@@

goby_out_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  xlab("Experimental phase relative to noise exposure")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(),  
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))

@@

goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),  
        axis.text.x = element_text(size = 13),
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke") +
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))

@@

goby_out_plot3
ggsave("./3-figs/goby_out_plot3.png", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

###2.3.4 Effects of covariates on the proportion of time gobies spent outside of the burrow
####2.3.4.1 Goby number
```{r}
goby_out_goby_number <- goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

@@

shrimp_out_model <- brm(
  shrimp_out_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 12345,
  file = "shrimp_out_model"
)

@@

###2.4.2 Posterior marginal effects
####2.4.2.1 Pairwise contrasts of stroke and stage
```{r}
shrimp_out_contrasts <- shrimp_out_model |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

@@

shrimp_out_fig_control <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  labs(x="Period relative to treatment",
       y="Proportion of time out of burrow") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_text(size = 13),
        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))

@@

shrimp_out_fig_four <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  xlab("Experimental phase relative to noise exposure")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(),  
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))

@@

shrimp_out_fig_two <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),  
        axis.text.x = element_text(size = 13),
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke") +
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))

@@

shrimp_out_plot3
ggsave("./3-figs/shrimp_out_plot3.png", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

shrimp_out_shrimp_number_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

ggplot(data = shrimp_out_shrimp_number_contrasts, aes(x = contrast, y = .value )) +
  stat_halfeye()
```
####2.4.4.3 Shrimp species
```{r}
shrimp_out_shrimp_species_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

@@

shrimp_out_shrimp_species_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

ggplot(data = shrimp_out_shrimp_species_contrasts, aes(x = contrast, y = .value )) +
  stat_halfeye()
```

@@

###2.5.2 Running the model
```{r}
shrimp_contact_model <- brm(
  bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
     ),
  data = final_df,
  prior = priors,
  family = zero_one_inflated_beta(),
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  chains = 4, iter = 6000, warmup = 1000, seed = 12345, backend = "cmdstanr", cores = 4, threads = threading(2),
  file = "shrimp_contact_model"
)

@@

@@

shrimp_contact_plot3
ggsave("./3-figs/shrimp_contact_plot3.png", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

#Alternate graphs
## Goby out
```{r}
goby_out_model_draws <- goby_out_model |> 
  emmeans(~ stroke*stage,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA) |> 
  gather_emmeans_draws()

>>>>

loc_normal <- 0
scale_normal <- 3

@@

# Plot the PDFs
df <- data.frame(x = x, Logistic = pdf_logistic, Student_t = pdf_student_t, Normal = pdf_normal)
ggplot(df, aes(x)) +
  geom_line(aes(y = Logistic, color = "Logistic(0, 3)")) + # Default priors of Logistic(0,1) have been broadened as these priors seemed too restrictive
  geom_line(aes(y = Student_t, color = "Student_t(3, 0, 2.5)")) +
  geom_line(aes(y = Normal, color = "Normal(0, 3)")) + #For the beta coefficient prior, we will set it to be normally distributed around 0 with an sd of 5, here is the plotted prior distribution 
  labs(title = "Probability Density Functions",
       x = "x",
       y = "Probability Density") +
  scale_color_manual(name = "Distribution", values = c("Logistic(0, 3)" = "blue", "Student_t(3, 0, 2.5)" = "green", "Normal(0, 3)" = "red")) +
  theme_minimal()
```

###2.2.4 Setting priors 
```{r}
#the priors for the intercept have been left as the default and the coefficient priors defined above
priors <- c(set_prior("student_t(3, 0, 2.5)", class = "Intercept"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "coi"),
            set_prior("logistic(0, 3)", class = "Intercept", dpar = "zoi"),
            set_prior("student_t(3, 0, 2.5)", class = "Intercept", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "phi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "zoi", lb = 0),
            set_prior("student_t(3, 0, 2.5)", class = "sd", dpar = "coi", lb = 0),
            set_prior("normal(0, 3)", class = "b"),
            set_prior("normal(0, 3)", class = "b", dpar = "phi"),
            set_prior("normal(0, 3)", class = "b", dpar = "zoi"),
            set_prior("normal(0, 3)", class = "b", dpar = "coi"))
```

@@

prior_model <- brm(
  prior_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 1000, warmup = 100,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1,
  sample_prior = "only",
  file = "prior_check"
)

@@

goby_out_model <- brm(
  goby_out_formula_1,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1,
  file = "goby_out_model"
)

@@

goby_out_fig_control <- ggplot(goby_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  labs(x="Period relative to treatment",
       y="Proportion of time out of burrow") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_text(size = 13),
        panel.grid = element_blank(),
        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))

@@

goby_out_fig_four <- ggplot(goby_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  xlab("Experimental phase relative to noise exposure")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(),  
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))

@@

goby_out_fig_two <- ggplot(goby_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = goby_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = goby_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = goby_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = goby_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),  
        axis.text.x = element_text(size = 13),
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        panel.grid = element_blank(),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke") +
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))

@@

goby_out_plot3
ggsave("./3-figs/goby_out_plot3.jpeg", plot = goby_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

###2.3.4 Effects of covariates on the proportion of time gobies spent outside of the burrow
####2.3.4.1 Goby number
```{r}
goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL)

goby_out_goby_number <- goby_out_model |>
  emmeans(~ goby_number, 
          epred = TRUE,
          re_formla = NULL) |> 
  contrast(method = "revpairwise")

@@

shrimp_out_model <- brm(
  shrimp_out_formula,
  data = final_df,
  family = zero_one_inflated_beta(),
  prior = priors,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 12),
  chains = 4, iter = 4000, warmup = 1000,
  cores = 4, threads = threading(2),
  backend = "cmdstanr",
  seed = 1,
  file = "shrimp_out_model"
)

@@

###2.4.2 Posterior marginal effects
####2.4.2.1 Pairwise contrasts of stroke and stage
```{r}
ranef(shrimp_out_model)

shrimp_out_contrasts <- shrimp_out_model |>
  emmeans(~ stroke*stage, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

@@

shrimp_out_fig_control <- ggplot(shrimp_control_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_control, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_control, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = shrimp_control_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  labs(x="Period relative to treatment",
       y="Proportion of time out of burrow") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(), 
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_text(size = 13),
        panel.grid = element_blank(),
        axis.title.y = element_text(size = 16, face = "bold", margin = margin(t = 0, b = 0, l = 0, r = 10)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#A3C088", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("Control")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#76A34A", "Post" = "#D3D9A7")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#2A330E", "Post" = "#5d634c"))

@@

shrimp_out_fig_four <- ggplot(shrimp_four_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_four, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_four, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = shrimp_four_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  xlab("Experimental phase relative to noise exposure")+
  theme(legend.position = "none", 
        axis.title.y = element_blank(),  
        axis.text.x = element_text(size = 13),  
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        panel.grid = element_blank(),
        axis.title.x = element_text(size = 16, face = "bold", margin = margin(t = 15, b = 0, l = 0, r = 0)),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#F6BC65", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("4-stroke")+
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#F29E00", "Post" = "#F2D5A0")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#805213", "Post" = "#70532b"))

@@

shrimp_out_fig_two <- ggplot(shrimp_two_raw_data, aes(y = .value, x = stage, fill = stage, color = stage)) +
  geom_half_violin(data = shrimp_out_control_model_draws, alpha = 0.7, size = 0, side = "r", position = position_nudge(x = 0.2)) +
  geom_jitter(position = position_jitternudge(x = -0.1, width = 0.1, nudge.from = "jittered"), alpha = 0.4, size = 2) +
  geom_crossbar(alpha = 0.6, size = 0.8, data = shrimp_out_model_estimates_two, aes(ymin = lower.HPD, ymax = upper.HPD), width = 0, position = position_nudge(x = 0.2))+
  geom_point(pch = 23, stroke = 1.2, data = shrimp_out_model_estimates_two, size = 2, position = position_nudge(x = 0.2)) +
  geom_point(data = shrimp_two_means, position = position_dodgenudge(width = 0.8, x = -0.1), size = 9, shape = "_") +
  theme(legend.position = "none", 
        axis.title.x = element_blank(),  
        axis.text.x = element_text(size = 13),
        axis.title.y = element_blank(), 
        axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        panel.grid = element_blank(),
        plot.title = element_textbox_simple(face = "bold", size = 16, halign = 0.5, linewidth = 0.3, linetype = 1, color = "black", fill = "#EB9063", padding = margin(5, 5, 5, 5)), 
        panel.background = element_rect(fill = "white", colour = "black"),
        plot.background = element_rect(fill = NA, colour = NA))+
  ggtitle("2-stroke") +
  scale_fill_manual(values = c("Pre" = "darkgrey", "During" = "#E25A00", "Post" = "#F2B389")) +
  scale_color_manual(values = c("Pre" = "#242424", "During" = "#542709", "Post" = "#66422a"))

@@

shrimp_out_plot3
ggsave("./3-figs/shrimp_out_plot3.jpeg", plot = shrimp_out_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

shrimp_out_shrimp_number_contrast_draws <- shrimp_out_model |>
  emmeans(~ shrimp_number, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

ggplot(data = shrimp_out_shrimp_number_contrast_draws, aes(x = contrast, y = .value )) +
  stat_halfeye()
```
####2.4.4.3 Shrimp species
```{r}
shrimp_out_shrimp_species_contrasts <- shrimp_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise")

@@

shrimp_out_shrimp_species_contrasts_draws <- shrimp_out_model |>
  emmeans(~ shrimp_species, 
          epred = TRUE,
          re_formla = NULL,
          rg.limit =14000) |> 
  contrast(method = "revpairwise") |> 
  gather_emmeans_draws()

ggplot(data = shrimp_out_shrimp_species_contrasts_draws, aes(x = contrast, y = .value )) +
  stat_halfeye()
```

@@

###2.5.2 Running the model
```{r}
shrimp_contact_model <- brm(
  bf(shrimp_contact ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     phi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     zoi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow),
     coi ~ stroke*stage + shrimp_number + goby_number + shrimp_species + (1|site/burrow)
     ),
  data = final_df,
  prior = priors,
  family = zero_one_inflated_beta(),
  control = list(adapt_delta = 0.99, max_treedepth = 12),
  chains = 4, iter = 6000, warmup = 1000, seed = 1, backend = "cmdstanr", cores = 4, threads = threading(2),
  file = "shrimp_contact_model"
)

@@

shrimp_contact_model |> 
  emmeans(~ 1,
          epred = TRUE,
          rg.limit = 14000,
          re_formula = NA)

@@

shrimp_contact_plot3
ggsave("./3-figs/shrimp_contact_plot3.jpeg", plot = shrimp_contact_plot3, units = "px", width = 2200, height = 1400, dpi = 300)
```

@@

#3 Manuscript output files
##3.1 Supp tables
###3.1.1 Model estimates
```{r}
goby_out_model_estimates <- goby_out_model_estimates |> 
  mutate(`Behavioural measure` = "Proportion of time gobies spent outside of the burrow")
